A Web Application for Wildlife Sightings - how accessible is this technology using modern frameworks?

### 2024-12-18 article/main.tex
update .gitignore to exclude 'bericht/' directory; normalize keywords in main.tex
Discussion section written

% Add 5-10 keywords for every submission
\keywords{Web Application, Wildlife Sightings, Geodata, Field Recording, Web Frameworks}

@@

>>>>

% Add 5-10 keywords for every submission
\keywords{web application, wildlife sightings, geodata, field recording, web frameworks}

@@

It seems that the technology to create a web application to record geo tagged data is accessible to everyone with a bit more than basic programming knowledge,
some help and some insane persistence. The app was successfully developed and deployed. The data view was created and the data can be accessed via a REST API.
Still it was a real struggle to get to this point and the hours put into this project are countless. The technology is accessible but the learning curve is steep.
It is hard to determine if the accessability is more a result of modern frameworks or the fast improving AI tools like GitHub Copilot and ChatGPT.

The biggest challenge was to keep an overview of all the components and how they interact with each other. For every part of the app there are countless
files and modules somehow connected to each other. Especially the frontend was a real struggle. After the simple command \texttt{ionic start} and
taking a few initial decisions, the project folder initiated by the framework is already filled with a lot of files and folders rather cryptic to a beginner. While AI is
very strong in writing functions or limited parts of the code it is not very helpful in keeping an overview of the whole project.
That seems to be where the real challenge lies.

\subsection{Next Steps}

The App is at this point a working prototype. A first step would be to further clean up the code and make it more readable before adding more to it.
There are a few things that would need some more work. A especially important one would be the spatial data and its accuracy.
Questions to follow up on would be: Is there a way to maximize the accuracy of the phone location? 
How to handle the accuracy of the manually imputed location?
An other important thing to work on would be the app control elements. While the idea was to keep the app as simple as possible,
a bit more control would be nice. For example the possibility to go back to the previous screen to change the input.
A data view within the app could be a nice feature especially the option to delete data points
in order for the user to correct mistakes.

In order for this things to be implemented and the project being taken further, an actual use case would be needed.
It can be a bit frustrating to work on a project, intense like this one, without a real use case.
With an actual use case there would be a clear goal and therefore a clear path to follow. For example the
data structure would not be as generic and some real considerations there could improve the app.
An other very important thing provided by a real use case would be an actual user group testing the app.
